Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis.

### 2018-06-20 manuscript/02_methods.Rmd
Minor text revisions

The R code and ancillary data for running these analyses is publicly available online via the Open Science Framework (OSF) at <https://osf.io/w8y73/>.
The TRY data used for this analysis can be requested at <http://try-db.org>.

>>>>

The R code and ancillary data for running these analyses is publicly available online via the Open Science Framework (OSF) at <https://osf.io/w8y73/>.
The TRY data request used for this analysis has been archived at <http://try-db.org>,
and can be retrieved by providing the request ID (#1584).
Alternatively, the exact pre-formatted data used in this analysis are available on request to Alexey Shiklomanov (ashiklom@bu.edu).
